Capitalized Title Here

### 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
added figure captions, added figure 1_v2

```{=tex}
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\wj}[1]{{\textcolor{forestgreen}{#1}}}
\setlength{\parindent}{0pt}
```

@@

@@

```{r, echo=FALSE, out.width="400px", fig.cap="figure captions \\hh{it'd be also good to put in labels for each state. I've added a huge arrow to help with the directionality (Stacy said she had trouble) - I like the way you have the order, it might just need some emphasis. What do you think of adding a bigger arrow (or arrows) in the back?}"}
knitr::include_graphics("img/figure1.png", dpi = 100)
```

Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score. The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps] in 2019, is one such algorithm. The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values. Then the congruent registration position is the position where the most basis segments find it the "best", and the number of basis segments taking the congruent registration position is the CMPS score. The CMPS algorithm can assist firearm examiners with drawing a conclusion, but NIST's implementation of the CMPS algorithm was not released for the public. Thus, in this paper we present an open-source implementation of the CMPS algorithm so that everyone can use and improve it. With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

```{r, echo=FALSE, out.width="300px"}
knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px"}
knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px"}
knitr::include_graphics("img/segplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px"}
knitr::include_graphics("img/segplot2.png", dpi = 100)
```

Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segments.

@@

```{r, echo=FALSE, out.width="400px"}
knitr::include_graphics("img/segplot3.png", dpi = 100)
```

>>>>

```{=tex}
\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
\setlength{\parindent}{0pt}
```

@@

In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method. @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its usage in examples of comparing bullet signature correlations. Although @cmps introduced the algorithm of the CMPS method in their paper, an open-source implementation of this powerful method was missing. Thus, our effort here is to introduce the CMPS method to `R` community and provide an open-source implementation of the algorithm for people to use and make further improvements. Our implementation was wrapped up into a `R` package called `CMPS`, which is available on GitHub[cite git?]. In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps and implemented the CMPS algorithm, and present results of applying our implementation to real data.

@@

```{r, echo=FALSE, out.width="400px", fig.cap="image of a XXX gun barrel and a fired bullet"}
knitr::include_graphics("img/barrel_bullet.PNG", dpi = 100)
```

```{r, echo=FALSE, out.width="400px", fig.cap="figure captions \\hh{it'd be also good to put in labels for each state. I've added a huge arrow to help with the directionality (Stacy said she had trouble) - I like the way you have the order, it might just need some emphasis. What do you think of adding a bigger arrow (or arrows) in the back?} (a) front view of a scanned land engraved area (LEA). The optimized crosscut location is indicated by the white line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves (d) the crosscut data after chopping the left and right grooves (e) the fitted curvature using LOESS (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
```

Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score. The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps], is one such algorithm. The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values. Then the congruent registration position is the position where the most basis segments find it the "best", and the number of basis segments taking the congruent registration position is the CMPS score. The CMPS algorithm can assist firearm examiners with drawing a conclusion, but NIST's implementation of the CMPS algorithm was not released for the public. Thus, in this paper we present an open-source implementation of the CMPS algorithm so that everyone can use and improve it. With our implementation, one can compute the CMPS score of a comparison using the following code:

@@

```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment. "}
knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; the red line shows the reference profile. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="segment_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments. "}
knitr::include_graphics("img/segplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="scale_ccf_plot shows the cross-correlation curve between the comparison profile and segment 6 at scale 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone. We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"}
knitr::include_graphics("img/segplot2.png", dpi = 100)
```

Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segment.

@@

```{r, echo=FALSE, out.width="400px", fig.cap="put segment_plot and scale_ccf_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."}
knitr::include_graphics("img/segplot3.png", dpi = 100)
```
